Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-16 paper/paper.tex
Bounds on OPT

  Now we lower-bound the cost of $\OPT$.
  By $\OPT(\sigma_I)$ and $\OPT(\sigma_E)$ we denote the cost of $\OPT$ on these input sequences ($\sigma_I$ and $\sigma_E$ are defined with respect to components of \TAlg in this phase).
  By $\OPT(M)$ we denote the cost of migrations performed by $\OPT$ in this phase.

@@

  %First, we estimate the cost related to $\sigma_I$.
  We have $OPT(M) + OPT(\sigma_I) \geq \alpha$, as the components of \TAlg{} could not be partitioned without splitting them, and there exists a pair of nodes with at least $\alpha$ requests between them.
  $\OPT$ either served them remotely or performed a~migration.

>>>>

  Now we lower-bound the cost of $\OPT$.
  By $\OPT(\sigma_I)$ and $\OPT(\sigma_E)$ we denote the cost of $\OPT$ on these input sequences (defined with respect to components of \TAlg in this phase).
  By $\OPT(M)$ we denote the cost of migrations performed by $\OPT$ in this phase.

@@

  %First, we estimate the cost related to $\sigma_I$.
  We have $OPT(M) + OPT(\sigma_I) \geq \alpha$, as the phase ended when the components of \TAlg{} could not be partitioned without splitting them.
  Hence, for every possible configuration of $\OPT$, there exists a non-collocated pair of nodes with at least $\alpha$ requests between them, and
  $\OPT$ either served them remotely or performed a~migration.
